Figures to insert in text

### 2018-03-07 Chapters/Chapter02.tex
SDM

\begin{figure}[h!]
  \centering
  \subfloat[$z \in \{.1, .2, .3, .4, .5, 1\}$]{\includegraphics[width=3.2in]{./images02/new-images/iter_z_01-05.png}}

  \subfloat[$z \in \{1.5, 3, 4.5, 6\}$]{\includegraphics[width=3.2in]{./images02/new-images/z_15_3_45_6.png}}

@@

\chapter{Results (ii): Performance}

>>>>

In this chapter we will explore how the generalized read operation works and whether it may improve SDM behavior. In this case, we understand that SDM behavior will have been improved when the critical distance increases, which means it is able to recognize things with even less clues than before.

In Figure

\begin{figure}[h!]
  \centering
  \subfloat[SDM behavior when $z \in \{0.1, 0.2, 0.3, 0.4, 0.5, 1\}$ ]{\includegraphics[width=\textwidth]{./images02/new-images/iter_z_01-05.png}}

  \subfloat[SDM behavior when $z \in \{1.5, 3, 4.5, 6\}$ ]{\includegraphics[width=\textwidth]{./images02/new-images/z_15_3_45_6.png}}

@@

\chapter{Results (iv): Performance}
